Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-06-27 SupportingInformation.Rmd
changes in code

```{r bivar_tab_summary_fn,echo=F}
bivar_tab_summary_fn<-function(r,rs){

  m<-matrix(NA,1,12)
  colnames(m)<-c("Indep.p","AIC-best.copula","Highest.AICw",
                 "N.AICw","p.CvM","p.KS",
                 "LT_model.avg","UT_model.avg","(LT-UT)_model.avg",
                 "Rank_Pl_surrog","Rank_Pu_surrog","Rank_Pl-Pu_surrog")
  m<-as.data.frame(m)

  m$Indep.p<-round(r$IndepTestRes,3)
  m$`AIC-best.copula`<-r$InfCritRes$copname[which.min(r$InfCritRes$AIC)]
  m$Highest.AICw<-round(max(r$InfCritRes$AICw),3)
  m$N.AICw<-round(r$InfCritRes$AICw[1],3)
  m$p.CvM<-r$GofRes_CvM
  m$p.KS<-r$GofRes_KS
  m$LT_model.avg<-round(r$relLTdep_AICw,3)
  m$UT_model.avg<-round(r$relUTdep_AICw,3)
  m$`(LT-UT)_model.avg`<-m$LT_model.avg-m$UT_model.avg
  m$Rank_Pl_surrog<-NA
  m$Rank_Pu_surrog<-NA
  m$`Rank_Pl-Pu_surrog`<-NA
  mt<-as.data.frame(t(m))
  return(mt)

>>>>

```{r bivar_tab_summary_fn,echo=F}
bivar_tab_summary_fn<-function(r){

  m<-matrix(NA,1,12)
  colnames(m)<-c("Indep.p","AIC-best.copula","Highest.AICw",
                 "N.AICw","p.CvM","p.KS",
                 "LT_model.avg","UT_model.avg","(LT-UT)_model.avg",
                 "Rank_Pl_K","Rank_Pu_K","Rank_Pl-Pu_K")
  m<-as.data.frame(m)

  m$Indep.p<-round(r$IndepTestRes,3)
  m$`AIC-best.copula`<-r$InfCritRes$copname[which.min(r$InfCritRes$AIC)]
  m$Highest.AICw<-round(max(r$InfCritRes$AICw),3)
  m$N.AICw<-round(r$InfCritRes$AICw[1],3)
  m$p.CvM<-r$GofRes_CvM
  m$p.KS<-r$GofRes_KS
  m$LT_model.avg<-round(r$relLTdep_AICw,3)
  m$UT_model.avg<-round(r$relUTdep_AICw,3)
  m$`(LT-UT)_model.avg`<-m$LT_model.avg-m$UT_model.avg
  m$Rank_Pl_K<-r$Rank_Pl_K
  m$Rank_Pu_K<-r$Rank_Pu_K
  m$`Rank_Pl-Pu_K`<-r$Rank_PlmPu_K
  mt<-as.data.frame(t(m))
  return(mt)
